---
title: "Markdown Excercise"
author: "My Name"
date: "6/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gapminder)
```

## The Gapminder Data Set

The structure of the gapminder data-set is as follows:

```{r}


```


## The Life Expectancy across continents

In 2002 the mean life expectancy for each continent is:

```{r}


```

## Gross Domestic Product

The 10 countries with the highest GDP per capita in 2007 are:

```{r}


```

How does this compare to the 10 countries with the highest total GDP (gdpPercap multiplied by population) in 2007. These are:

```{r}



```


## Relationship bewteen GDP per Capita and life Expectancy

We can plot GDP Per cap against life expectancy for each year to better understand the relationship. 

```{r pressure}



```

The **take-home message** from this plot is that:

> There is a relationship between gdpPercap and life expectancy so that countries with lower gdpPercap have lower life expectancy.
